Disease Knowledge Transfer across Neurodegenerative Diseases

### 2019-10-08 paper/pres/poster-dkt.tex
minor

\heading{Aim}\;\;\;\;Infer progression of multimodal biomarkers in rare neurodegenerative diseases (NDs) by leveraging larger datasets of common NDs.

\heading{Why}\;\;\;\;Posterior Cortical Atrophy (PCA): progression of \underline{multimodal} biomarkers not known $\rightarrow$ Identify outcome measures and suitable subjects for PCA clinical trials

@@

\begin{itemize}
 \item Diseases affect different brain regions un-equally, but underlyining mechanisms are the same (amyloid cascade)
 \item \textbf{Idea:} each brain region follows ``its own disease course'', common across diseases $\rightarrow$ dysfunction score
\end{itemize}

>>>>

\heading{Aim:}\;\;\;\;Infer progression of multimodal biomarkers in rare neurodegenerative diseases (NDs) by leveraging larger datasets of common NDs.

\heading{Why:}\;\;\;\;Posterior Cortical Atrophy (PCA): progression of \underline{multimodal} biomarkers not known $\rightarrow$ Identify outcome measures and suitable subjects for PCA clinical trials.

@@

\begin{itemize}
 \item Diseases affect different brain regions un-equally, but underlyining mechanisms are the same (amyloid cascade).
 \item \textbf{Idea:} each brain region follows ``its own disease course'', common across diseases.
\end{itemize}
